---
title: "US Higher Education Institutions"
subtitle: "Plotly Practice"
author: "Armen Abnousi"
date: "July 12, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
setwd("~/coursera/coursera_developing_data_products/week2_pa/")
knitr::opts_chunk$set(echo = TRUE)
```
<style>

.footer {
    color: black; background: white;
    position: fixed; top: 90%;
    text-align:left; width:100%;
}

</style>

## Data Source and Map Properties
For this exercise I aquired data from: 

+ [NCES IPEDS data inventory](https://nces.ed.gov/ipeds/datacenter/data/HD2015.zip) 

+ Hovering your mouse over the points will show their:
    1. latitude/langitude
    2. name
    3. webpage
        
+ You can also zoom in or out of the map
+ Check [Github](https://github.com/armensly/plotly_practice) for the code 


```{r echo = FALSE, message = FALSE, warning = FALSE}
nces_schools <- read.csv("../week2_pa/data/nces/hd2015.csv", stringsAsFactors = FALSE, fileEncoding = "CP1252")
nces_schools$LONGITUD <- as.numeric(nces_schools$LONGITUD)
nces_schools$LATITUDE <- as.numeric(nces_schools$LATITUDE)
nces_schools[458, "LONGITUD"] <- -121.925678
nces_schools[458, "LATITUDE"] <- 37.477779
```

## US Higher Education Institutions 

```{r, echo=FALSE, message = FALSE}
library(plotly)
library(keyringr)
my_mapbox_token <- decrypt_gk_pw("db mapbox user armen")
Sys.setenv('MAPBOX_TOKEN' = my_mapbox_token)

p <- plot_mapbox(nces_schools, type = "scattermapbox", mode = "scattermapbox") %>%
  add_markers(
    x = ~LONGITUD, y = ~LATITUDE, text = ~paste(nces_schools$INSTNM, "\nwebpage: ", nces_schools$WEBADDR), 
    marker = list(symbol = "circle", size = 6, opacity = 0.5), showlegend = FALSE, hoverinfo = "lat+lon+text",
  ) %>%   layout(
    mapbox = list(
     center = list(lat = ~median(nces_schools$LATITUDE), lon = ~median(nces_schools$LONGITUD)),
     style = "streets", zoom = 2
    )
  )
p
```

## More Details... 

- *Plotly* can use a set of tools from [mapbox.com](https://www.mapbox.com)
- For this plot I have used **plot_mapbox(...)** function from the plotly package
- In order for plotly package to use the *mapbox* toolset, the user needs a MAPBOX access token (free)
- I have used the *keyringr* package to hide my password from showing in the code (to upload on Github)